Pillar 1 - Sequential Pattern Mining

### 2019-02-06 Pillar 1 - Sequential Pattern Mining.Rmd
simplify code
d_support_G

#
# Probability of taking a course
d_support_take <- d_transactions %>%
  distinct(
    item,
    sequenceID
    ) %>%
  count(
    item
    ) %>%
  mutate(
    rate.take = n / n_students,
    rate.not  = 1 - rate.take
    )

#
# Probability of failing, having a low grade, having a grade less than x per course
d_support <- d_transactions %>%
  group_by(
    item
    ) %>%
  summarise(
    rate.fail = mean(PF == "fail"),
    rate.low  = mean(HL == "low"),
    rate.0    = mean(Grade <= 0),
    rate.1    = mean(Grade <= 1),
    rate.2    = mean(Grade <= 2),
    rate.3    = mean(Grade <= 3),
    rate.4    = mean(Grade <= 4),
    rate.5    = mean(Grade <= 5),
    rate.6    = mean(Grade <= 6),
    rate.7    = mean(Grade <= 7),
    rate.8    = mean(Grade <= 8),
    rate.9    = mean(Grade <= 9),
    rate.10   = mean(Grade <= 10)
    )

@@

```{r AR grade (by hand)}

#
# d_support
d_support_grade <- d_support %>%
  gather(
    key   = grade_round,
    value = support.grade,
    rate.0, rate.1, rate.2, rate.3, rate.4, rate.5, rate.6, rate.7, rate.8, rate.9, rate.10
    ) %>%
  mutate( 
    grade_round = substr(grade_round, start = 6, stop = 7),
    grade_round = as.numeric(grade_round)
    ) %>%
  select(-c(rate.fail, rate.low))

# Make AR
AR_G <- transactions_G %>%
  my_apriori(appearance = NULL) %>%
  clean_AR %>%

>>>>

#
# Probability of taking a course
d_support_TNT <- d_transactions %>%
  distinct(
    item,
    sequenceID
    ) %>%
  count(
    item
    ) %>%
  mutate(
    rate.take = n / n_students,
    rate.not  = 1 - rate.take
    )

#
# Probability of failing, having a low grade, having a grade less than x per course
d_support_PF_HL <- d_transactions %>%
  group_by(
    item
    ) %>%
  summarise(
    rate.fail = mean(PF == "fail"),
    rate.low  = mean(HL == "low")
    )

#
# Probability oh having a grade equal or lower than x
d_support_G <- d_transactions %>%
  group_by(
    item
    ) %>%
  summarise(
    `0`    = mean(Grade <= 0),
    `1`    = mean(Grade <= 1),
    `2`    = mean(Grade <= 2),
    `3`    = mean(Grade <= 3),
    `4`    = mean(Grade <= 4),
    `5`    = mean(Grade <= 5),
    `6`    = mean(Grade <= 6),
    `7`    = mean(Grade <= 7),
    `8`    = mean(Grade <= 8),
    `9`    = mean(Grade <= 9),
    `10`   = mean(Grade <= 10)
    ) %>%
  gather(
    key   = grade_ceil,
    value = support.grade,
    `0` : `10`,
    convert = TRUE
    )

@@

```{r AR grade}
AR_G <- transactions_G %>%

  my_apriori(appearance = NULL) %>%
  clean_AR %>%
